GEE models

### 2017-07-20 doc/manuscript.Rmd
minor removal of extra commented code

```{r captions}
## Include captions below using `captioner` package
library(captioner)
fig <- captioner(prefix = 'Fig.')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner(prefix = 'ESM Fig.')
cite_sf <- pryr::partial(sfig, display = 'cite')
tab <- captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner(prefix = 'ESM Table')
cite_st <- pryr::partial(stab, display = 'cite')
# usage: cite_st('basicChar')

>>>>

```{r captions}
## Include captions below using `captioner` package
library(captioner)
fig <- captioner(prefix = 'Fig.')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner(prefix = 'ESM Fig.')
cite_sf <- pryr::partial(sfig, display = 'cite')
tab <- captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner(prefix = 'ESM Table')
cite_st <- pryr::partial(stab, display = 'cite')
